Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-09 discussion.tex
...

  However, the presented approach also comes with several limitations.

@@

  \subsection*{Lack of Proof of Adoptability}

@@

  \subsection*{Flexibility: Allowing Multiple Groupings}

    To be agile, a tool has to be easily adaptable to different usage scenarios.

    One of the current limitations is that one can only specify one type of grouping. 
    However, there could be cases where multiple groupins would be desirable.

    Grouping the information by client application that sends the request could be important as a complementary grouping even in the current \zee case study.

>>>>

  However, the presented approach also comes with several limitations. Some of these limitations might also represent challenges for the future builders of similar tools.

@@

  \subsection*{Lack of Empirical Proof of Ease of Adoptability}

@@

  \subsection*{Lack of Flexibility in Allowing Multiple Groupings}

    To be agile, a tool has to be easily adaptable to different usage scenarios. However, currently one of the current limitations of \tool is that that one can only specify one type of grouping. This is insufficient for the cases where multiple groupings are desirable. In the \zee case study this need emerged in the context in which it would be good to grouping the requests also by the client application that sends the request.
